A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-11 paper/ms.tex
update ms
figure formatting

minor text edits

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (lower-right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.}
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  The reported
cluster members (gray and black points) extend over a much larger
volume than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.  We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed the
selection cuts manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle
    is a candidate cluster member selected from the catalog of
    \citet{KounkelCovey2019} based on its position and kinematics.  Of
    the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

The previous analysis by \citet{holczer_transit_2016} did not
find any significant long-term transit timing or duration variations
for \sn\ (TTVs or TDVs).  Quantitatively, the mean and standard deviation of the
TTVs and TDVs they measured were $-1.1\pm13.8\,{\rm
min}$ and $-3.3\pm22.1\,{\rm min}$.  In an
earlier analysis however, \citet{holczer_time_2015} studied correlations
between TTVs and local light curve slopes, and for \sn\
found a weak correlation of $-29\pm13\,{\rm min}\,{\rm day}^{-1}$
between the two quantities.  While this constitutes only weak
statistical evidence, given the possible connection between such
correlations and the unresolved starspot crossings that we expect to
be present in the data for \sn\ \citep{mazeh_time_2015}, we opted to re-examine the
individual transit times.

@@

One concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
similar anti-correlations in the injected transits to that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below, however given the
statistical significance, this analysis should be interpreted as
suggestive at best.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}

@@

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  A 18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario would require an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm minutes}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra and {\it ii)} the lack of secondary
rotation signals in the Kepler photometry.

@@

The correlation noted in Section~\ref{subsec:ttvslope} between the
TTVs and the local light curve slope could be a further line of evidence
in support of the planetary interpretation.  Unless it is a
statistical fluke (a $\approx$5\% possibility), then its most likely
cause is unresolved starspot
crossings \citep{mazeh_time_2015}.  This would only be possible if the
planet transits the primary star, which excludes a background
eclipsing binary scenario.  It would also suggest that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this latter assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic (Figure~\ref{fig:ground}).
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
Kepler ephemeris and transit depth, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm minutes}$ shorter than the
Kepler transits.
However, given both the lack of transit duration variations in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure}

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Observations
of spectroscopic transits at greater precision should yield a
measurement of the stellar obliquity, which would confirm or refute
the prograde orbital geometry suggested by the TTV-local slope
correlation.  Separately, transit spectroscopy aimed at detecting
atmospheric outflows could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations that quantify the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  The most feasible
approach would likely be long-term monitoring of the transit times and
durations, given the technical difficulty of performing a multi-color
radial velocity campaign on a $V=13$ star.  Measured at
sufficient precision though, the mass, combined with the known age and
size, would yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This somewhat contrived geometry would be necessary in order to
explain why the starspot crossings would add up coherently.
Other possible explanations such as
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).  
Aside from the asymmetric transits, Appendix~\ref{app:flare}
highlights an additional abnormality in the short-cadence Kepler data, in the
arrival time distribution of stellar flares.  We encourage its
exploration by investigators more versed in the topic than ourselves.

@@

For any of the catalogs for which Gaia DR2 identifiers were not
available, we either followed the spatial (plus proper-motion)
cross-matching procedures described in \citet{bouma_cdipsI_2019}, or
else we pulled the Gaia DR2 source identifiers associated with the
catalog from SIMBAD.  We consequently opted to drop the
$\texttt{ext\_catalog\_name}$ and $\texttt{dist}$ columns maintained
in \citet{bouma_cdipsI_2019}, as these were only populated for a small
number of stars.  The technical manipulations for the merging,
cleaning, and joining were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual cross-match (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was
performed asychronously on the Gaia archive
website.\footnote{\url{https://gea.esac.esa.int/archive/}}

@@

We monitored \sn\ with Keck/HIRES before, during, and after transit on
the night of 2021 Aug 7.  We used the iodine cell for wavelength
calibration\footnote{We considered a line-profile based analysis in
the regions without iodine, but the line profile stability of HIRES
precludes such an approach.}, and extracted the 1-D spectra using the
standard California Planet Survey pipeline \citep{howard_cps_2010}.
The airmass ranged between 1.1 and 2.2 from the start through the end
of observations; the seeing ranged from $1\farcs1$ at the beginning to
$1\farcs5$ at the end.  We also simultaneously observed across {\it
griz} bands using MuSCAT3 at Haleakal\=a Observatory on Maui, HI.
Performing aperture photometry on the latter image stack yielded the
data given in Table~\ref{tab:phot}.

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom row) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  The reported
cluster members (gray and black points) extend over a much larger
volume than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.  We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed the
selection cuts manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster, shown in equatorial
    	coordinates.} Each black circle
    is a candidate cluster member selected from the catalog of
    \citet{KounkelCovey2019} based on its position and kinematics.  Of
    the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

The previous analysis by \citet{holczer_transit_2016} did not
find any significant long-term transit timing or duration variations
(TTVs or TDVs) for \sn.  Quantitatively, the mean and standard deviation of the
TTVs and TDVs they measured were $-1.1\pm13.8\,{\rm
min}$ and $-3.3\pm22.1\,{\rm min}$.  In an
earlier analysis however, \citet{holczer_time_2015} studied correlations
between TTVs and local light curve slopes, and for \sn\
found a weak correlation of $-29\pm13\,{\rm min}\,{\rm day}^{-1}$
between the two quantities.  Given the possible connection between such
correlations and the unresolved starspot crossings that we expect to
be present in the data for \sn\ \citep{mazeh_time_2015}, we opted to re-examine the
individual transit times.

@@

One concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
statistical significance, this analysis should be interpreted as
suggestive at best.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}

@@

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  A 18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario requires an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm minutes}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the main cluster isochrone on the Gaia CAMD (Figure~\ref{fig:age}).

@@

The correlation noted in Section~\ref{subsec:ttvslope} between the
TTVs and the local light curve slope might be an additional line of evidence
in support of the planetary interpretation.  Unless it is a
statistical fluke (a $\approx$5\% possibility), then the most likely
cause of the correlation is unresolved starspot
crossings \citep{mazeh_time_2015}.  These would only be possible if the
planet transits the primary star, which excludes a background
eclipsing binary scenario.  The correlation would also suggest that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this latter assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic (Figure~\ref{fig:ground}).
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
ephemeris and transit depth from the Kepler data, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm minutes}$ shorter than the
Kepler transits.
However, given both the lack of transit duration variations in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Observations
of spectroscopic transits at greater precision should yield a
measurement of the stellar obliquity, which would confirm or refute
the prograde orbital geometry suggested by the TTV-local slope
correlation.  Separately, transit spectroscopy aimed at detecting
atmospheric outflows could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations that quantify the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass. Measured at
sufficient precision,
for instance through a multi-wavelength radial velocity campaign,
the combination of the size, mass, and age 
would yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This fairly contrived geometry would be needed in order to
explain why the starspot crossings could add up coherently.
Other possibilities including
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).

Beyond the asymmetric transits, Appendix~\ref{app:flare}
highlights an additional abnormality in the short-cadence Kepler data, in the
arrival time distribution of stellar flares.  We encourage its
exploration by investigators more versed in the topic than ourselves.

@@

For any of the catalogs for which Gaia DR2 identifiers were not
available, we either followed the spatial (plus proper-motion)
cross-matching procedures described in \citet{bouma_cdipsI_2019}, or
else we pulled the Gaia DR2 source identifiers associated with the
catalog from SIMBAD.  We consequently opted to drop the
$\texttt{ext\_catalog\_name}$ and $\texttt{dist}$ columns maintained
in \citet{bouma_cdipsI_2019}, as these were only populated for a small
number of stars.  The technical manipulations for the merging,
cleaning, and joining were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual cross-match (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was
performed asychronously on the Gaia archive
website.

@@

We monitored \sn\ with Keck/HIRES before, during, and after transit on
the night of 2021 Aug 7.  We used the iodine cell for wavelength
calibration, and extracted the 1-D spectra using the
standard California Planet Survey pipeline \citep{howard_cps_2010}.
The airmass ranged between 1.1 and 2.2 from the start through the end
of observations; the seeing ranged from $1\farcs1$ at the beginning to
$1\farcs5$ at the end.  We also simultaneously observed across {\it
griz} bands using MuSCAT3 at Haleakal\=a Observatory on Maui, HI.
Performing aperture photometry on the latter image stack yielded the
data given in Table~\ref{tab:phot}.
